Query Optimization for Dynamic Imputation

### 2017-07-08 paper/experiments.tex

\subsection{Data Sets}\label{subsec:datasets}
We collect three data sets for our experiments.
For all data sets, we selected a subset of the original attributes.
We also transform all data values to an integer representation by enumerating strings and transforming floating-point values into an appropriate range.

@@

\begin{sloppypar}
\textbf{Runtime vs. Base-table Imputation}\quad \Cref{fig:runtimes} summarizes the performance results. The quality-optimized
queries, with runtimes ranging from \runtimetreelowzero{} to \runtimetreehighzero{}, are an
order-of-magnitude faster than the baseline, with runtimes ranging from
\runtimetreelowbase{} to \runtimetreehighbase{}. We get another order-of-magnitude speedup when
optimizing for performance, achieving runtimes as low as \runtimetreelowone{} to
\runtimetreehighone{}. These speedups, ranging from \lowxalphazero{}x to 
\highxalphaone{}x, depending on $\alpha$ and query, constitute significant workflow improvements
for the analyst.
\end{sloppypar}

@@

In hot deck imputation, runtimes are also similar across $\alpha$, ranging from
\runtimehotdecklow{} to \runtimehotdeckhigh{} using dynamic imputation, as compared to
\runtimehotdecklowbase{} to \runtimehotdeckhighbase{} when imputing on the base table. In
this case, the cost of buffering tuples and sampling at random is negligible compared to the
rest of query execution. Relative errors using hot deck are close to zero, ranging from
\smapehotdecklow{}--\smapehotdeckhigh{}\%. (The exception is \Cref{q8} with $\alpha=1$, which has error
of \smapehotdeckhighoutlier{}\% and exhibits significant skew.) Since the baseline, in these
cases, is hot deck imputation on the base table, it is skew in the distributions arising from
filters and joins that often leads to larger errors. Indeed, \ProjectName{} yields
larger benefit when using relatively sophisticated, higher quality imputation algorithms as
opposed to simpler strategies that would even be quick to implement on the base table.

@@

\begin{figure}
\centering
\includegraphics[scale=0.4]{figures/pareto_frontiers_plot.png}
\caption{\review{
    \ProjectName{}'s final planner Pareto frontier for \Cref{q1} and \Cref{q6}. 
    For clarity, we have removed from the plot plans that provide nearly indistinguishable trade-offs in either dimension.
}
\label{fig:pareto-frontiers}
}
\end{figure}

>>>>

\subsection{Data Sets}\label{subsec:datasets}
We collect three data sets for our experiments.
For all data sets, we select a subset of the original attributes.
We also transform all data values to an integer representation by enumerating strings and transforming floating-point values into an appropriate range.

@@

\begin{sloppypar}
\textbf{Runtime vs. Base-table Imputation}\quad \Cref{fig:runtimes} summarizes the performance results. The quality-optimized
queries, with runtimes ranging from \runtimetreelowzero{} to \runtimetreehighzero{}, are an
order-of-magnitude faster than the baseline, with runtimes ranging from
\runtimetreelowbase{} to \runtimetreehighbase{}. We get another order-of-magnitude speedup when
optimizing for performance, achieving runtimes as low as \runtimetreelowone{} to
\runtimetreehighone{}. These speedups, ranging from \lowxalphazero{}x to 
\highxalphaone{}x depending on $\alpha$ and query, constitute significant workflow improvements
for the analyst.
\end{sloppypar}

@@

In hot deck imputation, runtimes are also similar across $\alpha$, ranging from
\runtimehotdecklow{} to \runtimehotdeckhigh{} using dynamic imputation, as compared to
\runtimehotdecklowbase{} to \runtimehotdeckhighbase{} when imputing on the base table. In
this case, the cost of buffering tuples and sampling at random is negligible compared to the
rest of query execution. Relative errors using hot deck are close to zero, ranging from
\smapehotdecklow{}--\smapehotdeckhigh{}\%. (The exception is \Cref{q8} with $\alpha=1$, which has error
of \smapehotdeckhighoutlier{}\% and exhibits significant skew.) Since the baseline, in these
cases, is hot deck imputation on the base table, it is skew in the distributions arising from
filters and joins that often leads to larger errors. Indeed, \ProjectName{} yields
larger benefits when using relatively sophisticated, higher quality imputation algorithms as
opposed to simpler strategies that would be quick to implement even on the base tables.

@@

\begin{figure}
\centering
\includegraphics[scale=0.4]{figures/pareto_frontiers_plot.png}
\caption{\review{
    \ProjectName{}'s final planner Pareto frontier for \Cref{q1} and \Cref{q6}. 
    For clarity, we have not shown plans that provide nearly indistinguishable trade-offs in either dimension.
}
\label{fig:pareto-frontiers}
}
\end{figure}
